Calendar-based graphics for visualising people's daily schedules

### 2017-07-12 main.Rmd
Tweaks of today

```{r time-series-plot, fig.height = 6, fig.cap = "Time series plot about the number of pedestrians over the year of 2016 at a selection of 3 sensors in the city of Melbourne. Coloured by the sensors, small multiples of lines show that the foot traffic varies from one sensor to another in terms of both time and number. The traffic, specifically at two train stations (Flagstaff Station and Flinders Street Station), is primarily driven by the commuters, as depicted in the graph."}
```

@@

We propose a new algorithm via linear algebra tools to go beyond the calendar-based heatmap. The approach is developed with these conditions in mind: (1) to make time of day present in addition to the existing temporal components such as day of week and day of year, (2) to add line graphs along with other types of glyphs to the visual toolkit, (3) to enable an overlaying plot consisting of multiple time series. The proposed algorithm has been implemented as the \code{frame_calendar} function in the \pkg{sugrrants} package [@R-sugrrants] using \proglang{R} [@R-base].

The remainder of the paper is organised as follows. Section \ref{sec:algorithm} demonstrates the construction of the calendar layout in detail. Section \ref{sec:opt} lists and describes the options that come with the \code{frame_calendar} function. Section \ref{sec:examples} presents some variations of its usage. Section \ref{sec:discussion} discusses the advantages and disadvantages of the method.

@@

Assuming that tidy data [@wickham2014tidy] is the underlining data structure, the \code{x} takes a variable that will be mapped to the x axis and the \code{y} mapped to the y axis for the later plotting. In Figure \ref{fig:flinders-2016}, for example, the \code{x} is the variable specifying the time of the day, and the \code{y} is the variable suggesting the hourly counts. The \code{date} argument is given by the date variable that determines the correct order in the calendar layout. We shall describe some of the arguments that control the graphics in different ways.

>>>>

```{r time-series-plot, fig.height = 6, fig.cap = "Time series plot about the number of pedestrians over the year of 2016 at a selection of 3 sensors in the city of Melbourne. Coloured by the sensors, small multiples of lines show that the foot traffic varies from one sensor to another in terms of both time and number. The weekly patterns look distincitve across these 3 sensors. There is an eye-catching spike occurred to State Library, which is caused by the annual event--White Night--on 20th of Feburary."}
```

@@

We propose a new algorithm via linear algebra tools to go beyond the calendar-based heatmap. The approach is developed with these conditions in mind: (1) to make time of day present in addition to the existing temporal components such as day of week and day of year, (2) to incorporate line graphs and other types of glyphs into the graphical toolkit for the calendar layout, (3) to enable an overlaying plot consisting of multiple time series. The proposed algorithm has been implemented as the \code{frame_calendar} function in the \pkg{sugrrants} package [@R-sugrrants] using \proglang{R} [@R-base].

The remainder of the paper is organised as follows. Section \ref{sec:algorithm} demonstrates the construction of the calendar layout in depth. Section \ref{sec:opt} lists and describes the options that come with the \code{frame_calendar} function. Section \ref{sec:examples} presents some variations of its usage. Section \ref{sec:discussion} discusses the advantages and disadvantages of the method.

@@

Assuming that tidy data [@wickham2014tidy] is the underlining data structure, the \code{x} takes a variable that will be mapped to the x axis and the \code{y} mapped to the y axis for the later plotting. In Figure \ref{fig:flinders-2016}, for example, the \code{x} is the variable specifying the time of the day, and the \code{y} is the variable suggesting the hourly counts. The \code{date} argument is given by the date variable that determines the correct order in the calendar layout. We shall describe some of the arguments that allow for different displays.

### 2017-07-12 main.tex
Tweaks of today

\caption[Time series plot about the number of pedestrians over the year of 2016 at a selection of 3 sensors in the city of Melbourne]{Time series plot about the number of pedestrians over the year of 2016 at a selection of 3 sensors in the city of Melbourne. Coloured by the sensors, small multiples of lines show that the foot traffic varies from one sensor to another in terms of both time and number. The traffic, specifically at two train stations (Flagstaff Station and Flinders Street Station), is primarily driven by the commuters, as depicted in the graph.}\label{fig:time-series-plot}
\end{figure}
\end{CodeChunk}

@@

We propose a new algorithm via linear algebra tools to go beyond the
calendar-based heatmap. The approach is developed with these conditions
in mind: (1) to make time of day present in addition to the existing
temporal components such as day of week and day of year, (2) to add line
graphs along with other types of glyphs to the visual toolkit, (3) to
enable an overlaying plot consisting of multiple time series. The
proposed algorithm has been implemented as the \code{frame_calendar}
function in the \pkg{sugrrants} package \citep{R-sugrrants} using
\proglang{R} \citep{R-base}.

The remainder of the paper is organised as follows. Section
\ref{sec:algorithm} demonstrates the construction of the calendar layout
in detail. Section \ref{sec:opt} lists and describes the options that
come with the \code{frame_calendar} function. Section \ref{sec:examples}
presents some variations of its usage. Section \ref{sec:discussion}
discusses the advantages and disadvantages of the method.

@@

Assuming that tidy data \citep{wickham2014tidy} is the underlining data
structure, the \code{x} takes a variable that will be mapped to the x
axis and the \code{y} mapped to the y axis for the later plotting. In
Figure \ref{fig:flinders-2016}, for example, the \code{x} is the
variable specifying the time of the day, and the \code{y} is the
variable suggesting the hourly counts. The \code{date} argument is given
by the date variable that determines the correct order in the calendar
layout. We shall describe some of the arguments that control the
graphics in different ways.

>>>>

\caption[Time series plot about the number of pedestrians over the year of 2016 at a selection of 3 sensors in the city of Melbourne]{Time series plot about the number of pedestrians over the year of 2016 at a selection of 3 sensors in the city of Melbourne. Coloured by the sensors, small multiples of lines show that the foot traffic varies from one sensor to another in terms of both time and number. The weekly patterns look distincitve across these 3 sensors. There is an eye-catching spike occurred to State Library, which is caused by the annual event--White Night--on 20th of Feburary.}\label{fig:time-series-plot}
\end{figure}
\end{CodeChunk}

@@

We propose a new algorithm via linear algebra tools to go beyond the
calendar-based heatmap. The approach is developed with these conditions
in mind: (1) to make time of day present in addition to the existing
temporal components such as day of week and day of year, (2) to
incorporate line graphs and other types of glyphs into the graphical
toolkit for the calendar layout, (3) to enable an overlaying plot
consisting of multiple time series. The proposed algorithm has been
implemented as the \code{frame_calendar} function in the \pkg{sugrrants}
package \citep{R-sugrrants} using \proglang{R} \citep{R-base}.

The remainder of the paper is organised as follows. Section
\ref{sec:algorithm} demonstrates the construction of the calendar layout
in depth. Section \ref{sec:opt} lists and describes the options that
come with the \code{frame_calendar} function. Section \ref{sec:examples}
presents some variations of its usage. Section \ref{sec:discussion}
discusses the advantages and disadvantages of the method.

@@

Assuming that tidy data \citep{wickham2014tidy} is the underlining data
structure, the \code{x} takes a variable that will be mapped to the x
axis and the \code{y} mapped to the y axis for the later plotting. In
Figure \ref{fig:flinders-2016}, for example, the \code{x} is the
variable specifying the time of the day, and the \code{y} is the
variable suggesting the hourly counts. The \code{date} argument is given
by the date variable that determines the correct order in the calendar
layout. We shall describe some of the arguments that allow for different
displays.
